% vim: set spell:

\chapter{Course Content Management}

\label{section:infrastructure}

\begin{quotation}

\footnotesize\sffamily\itshape

\begin{flushright}

\selectlanguage{russian}

Тяжело в учении, легко в бою; легко в учении, тяжело в бою.

\selectlanguage{english}

\smallbreak

(Tough in training, easy in battle; easy in training, tough in battle.)

\smallbreak

\upshape

--- ALEXANDER SUVOROV, Generalissimo of the Russian Empire (1729--1800)

\end{flushright}

\end{quotation}

The intent of this chapter is to propose a course content management system
(CCMS), allowing for interactive, automated assessment of student submissions.
We consider this because the current CCMS in use at DIKU does not seemingly
provide for easy hooks for student submissions, or even accessing and
processing course data on our own account.

Our approach in general, is to use the Git version control system for the basic
mechanism of content distribution. Teaching staff (and the assessment engine)
use Git to publish learning material, assignments, and feedback. Students use
Git to make submissions, and ultimately, collaborate on submissions.

Student data is encrypted and signed by the students. Access to the student
data is mandated through an additional access control layer. This way we can
ensure that student submissions indeed come from the students, and even if our
access control layer fails to deliver, student data stays protected.

% This chapter provides a high level overview of the chosen system
% architecture.  We justify our choices, as well as discusses some of their
% benefits and downsides.

% Overall, there are three types of servers involved: a key server, a Git
% server, and a test server. The communications between them and the students
% and teaching staff are roughly illustrated by \referToFigure{infrastructure}.
% Each type of server may in reality be a set of interconnected servers
% balancing loads among each other, but fulfilling together the role of a
% single server type.

% \includeFigure[0.75]{infrastructure}{Illustration of some of the system
% architecture. All communication happens over secure channels. Both students
% and staff interact with the key server and Git server, but students have
% considerably less permissive rights on each of the servers}

%\input{course-content-management/motivation}

%\input{course-content-management/key-server}

\input{course-content-management/git-server}

\input{course-content-management/openssh}

\input{course-content-management/git-hooks}

\input{course-content-management/users}

\input{course-content-management/gitolite}

\input{course-content-management/encrypted-git-repositories}

\input{course-content-management/attack-surface}

\input{course-content-management/discussion}

% \input{course-content-management/test-server}
