% vim: set spell:

\section{Influence}

Our specification has been highly influenced by \cite{sclater-howie-2003},
entitled `User requirement for the ``ultimate'' online assessment engine'.
Sclater \& Howie arrive at their requirements after extensive discussions with
a focus group of academic and technical staff, involved in the development and
deployment of online testing systems at the University of Strathclyde.

Their requirements generally represent the wishes of this focus group, and are
influenced by their experiences with earlier products and students.  It is also
worth noting that the focus group does not include students --- an important
user group.

A common idiom in software development is that ``ultimate'' systems may fail to
be useful for any one purpose. We have cut away some ``ultimate'' requirements
when deemed not useful to us.

In the end, our wishes and goals depart only slightly from theirs. We summarise
the major differences below:

\begin{itemize}

\item We are not interested in the construction of large question or ``item''
banks\cite{conole-warburton-2005}. These are collections of questions or
tasks, ready for compilation into assignments. The benefit of such banks is
ease of reuse and the development of high-quality questions or tasks.

We deem it as a useful anti-cheating technique not to allow easy reuse of
questions or tasks in general. This forces teachers to stay sharp, and
minimises the possibility of cheating.

\item Given the above, neither are we interested in the abilities to sell
questions or tasks constructed for assessment.

\end{itemize}
