% vim: set spell:

\begin{thebibliography}{9} % 9 if < 10 references, 99 if < 100 references, etc.

\bibitem[Wheeler, 2007]{why-oss-fs}

David A. Wheeler. \emph{Why Open Source Software / Free Software (OSS/FS,
FLOSS, or FOSS)? Look at the Numbers!}. Revised as of April 16, 2007. Retrieved
from \url{http://www.dwheeler.com/oss_fs_why.html} on March 7, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6NtSnvALX}.

\bibitem[CS2013]{cs2013}

ACM/IEEE-CS Joint Task Force on Computing Curricula. \emph{Computer Science
Curricula 2013}. December 2013. ACM Press and IEEE Computer Society Press.
Retrieved from
\url{http://ai.stanford.edu/users/sahami/CS2013/final-draft/CS2013-final-report.pdf}
on March 7, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6NtTXPH2s}.

\bibitem[EHEA (1999)]{ehea1999}

Joint declaration of the European Ministers of Education. \emph{The Bologna
Declaration}. June 19, 1999. The European Higher Education Area. Retrieved from
\url{http://www.ehea.info/Uploads/Declarations/BOLOGNA_DECLARATION1.pdf} on
March 9, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6Nwr8h8l7}.

\bibitem[CND (2004)]{cnd2004}

Sebastian Horst and Carl Winsløw. \emph{Undervisning i blokstruktur -
potentialer og risici}. April 1, 2004. DidakTips 5. Center for Natufagenes
Didaktik.  University of Copenhagen. Retrieved from
\url{http://www.ind.ku.dk/publikationer/didaktips/didaktips5/5.undervisningiblokstruktur-potentialerogrisicimedomslag.pdf}
on March 9, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6NwjYWlBi}.

\bibitem[BEK 814]{bek814}

Ministeriet for Forskning, Innovation og Videregående Uddannelser.
\emph{Bekendtgørelse om bachelor- og kandidatuddannelser ved universiteterne
(uddannelsesbekendtgørelsen)}. Ministerial Order no. 814 of December 19,
2013.  Retrieved from
\url{https://www.retsinformation.dk/Forms/R0710.aspx?id=160853} on March 9,
2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6NyGHXc4N}.

\bibitem[BEK 1520]{bek1520}

Ministeriet for Forskning, Innovation og Videregående Uddannelser.
\emph{Bekendtgørelse om bachelor- og kandidatuddannelser ved universiteterne
(uddannelsesbekendtgørelsen)}. Ministerial Order no. 1520 of December 19,
2013.  Retrieved from
\url{https://www.retsinformation.dk/Forms/R0710.aspx?id=160853} on March 9,
2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6Nx4DxLGL}.

\bibitem[BEK 666]{bek666}

Ministeriet for Forskning, Innovation og Videregående Uddannelser.
\emph{Bekendtgørelse om eksamen og censur ved universitetsuddannelser
(eksamensbekendtgørelsen)}. Ministerial Order no. 666 of June 24, 2012.
Retrieved from \url{https://www.retsinformation.dk/Forms/R0710.aspx?id=142560}
on March 10, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6NyI0DlqJ}.

\bibitem[BEK 250]{bek250}

Ministeriet for Forskning, Innovation og Videregående Uddannelser.
\emph{Bekendtgørelse om karakterskala og anden bedømmelse ved
universitetsuddannelser (karakterbekendtgørelsen)}. Ministerial Order no. 250
of March 15, 2007.  Retrieved from
\url{https://www.retsinformation.dk/Forms/R0710.aspx?id=29307} on March 11,
2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6NzVOdWtv}.

\bibitem[Curricula (2013)]{faelles-del-ENG}

\emph{The shared section of the BSc and MSc curricula for study programmes at
the Faculty of Science, University of Copenhagen}. September 2013. Retrieved
from
\url{http://www.science.ku.dk/studerende/studieordninger/faelles_sto/Faelles-del-ENG-2013-web.pdf/}
on March 10, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6NyEpPK67}.

\bibitem[Bradfoot \& Black (2004)]{first-ten-years}

Patricia Broadfoot and Paul Black. \emph{Redefining assessment? The first ten
years of assessment in education}. 2004. Assessment in Education: Principles,
Policy \& Practice, Vol. 11, No. 1, pp. 7--26. DOI:
10.1080/0969594042000208976. Retrieved from
\url{https://cmap.helsinki.fi/rid=1G5ND18R4-1QLJN7R-1SB} on March 16, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6O7OhF8LW}.

\bibitem[Pishghadam et al. (2014)]{assessment-and-burnout}

Reza Pishghadam, Bob Adamson, Shaghayegh Shayesteh Sadafian, and Flora L. F.
Kan. \emph{Conceptions of assessment and teacher burnout}. 2014. Assessment in
Education: Principles, Policy \& Practice, Vol. 21, No. 1, pp. 34--51. DOI:
10.1080/0969594X.2013.817382.

\bibitem[Harlen \& James (1997)]{formative-vs-summative}

Wynne Harlen and Mary James. \emph{Assessment and Learning: differences and
relationships between formative and summative assessment}. 1997. Assessment in
Education: Principles, Policy \& Practice, Vol. 4, No. 3, pp. 365--379. DOI:
10.1080/0969594970040304.

\bibitem[Butler (1988)]{butler1988}

Ruth Butler. \emph{Enhancing and understanding intrinsic motivation: the
effects of of task-involving and ego-involving evaluation on interest and
performance}. February 1988. British Journal of Educational Psychology, Vol.
58, No. 1, pp. 1--14.

\bibitem[Sadler (1989)]{sadler1989}

D.Royce Sadler. \emph{Formative assessment and the design of instructional
systems}. June 1989. Instructional Science, Vol. 18, No. 2, pp. 119--144.
Kluwer Academic Publishers. DOI: 10.1007/BF00117714

\bibitem[Bloom et al. (1971)]{bloom1971}

Benjamin S. Bloom, J. Thomas Hastings, and George F. Madaus. \emph{Handbook on
Formative and Summative Evaluation of Student Learning.} 1971. McGraw-Hili,
Inc. United States. Library of Congress Catalog Card Number 75129488. ISBN
0070061149.

\bibitem[Ramaprasad (1989)]{ramaprasad1989}

Arkalgud Rapaprasad. \emph{On the definition of feedback}. January 1989.
Behavioural Science, Vol. 28, No. 1, pp. 8--13.

\bibitem[Black \& William (1998)]{black-william-1998}

Paul Black and Dylan William. \emph{Assessment and Classroom Learning}. 1998.
Assessment in Education: Principles, Policy \& Practice, Vol. 5, No. 1, pp.
7--74. DOI: 10.1080/0969595980050102.

\bibitem[Gibbs \& Simpson (2004)]{gibbs-simpson-2004}

Graham Gibbs and Claire Simpson. \emph{Conditions Under Which Assessment
Supports Students' Learning}. May 2004. Learning and Teaching in Higher
Education, Issue 1. Retrieved from
\url{http://www2.glos.ac.uk/offload/tli/lets/lathe/issue1/issue1.pdf} on March
22, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OGkhvGyE}.

\bibitem[Ramsden (1992)]{ramsden-1992}

Paul Ramsden. \emph{Learning to Teach in Higher Education}. 1992. Routledge.
ISBN 0-415-06415-5.

\bibitem[Conole \& Warburton (2005)]{conole-warburton-2005}

Gr\'ainne Conole and Bill Warburton. \emph{A review of computer-assisted
assessment}. March 2005. The Journal of the Association for Learning Technology
(ALT-J), Research in Learning Technology, Vol. 14, No. 1, pp. 17--31. Retrieved
from
\url{http://www.researchinlearningtechnology.net/index.php/rlt/article/download/10970/12674}
on March 23, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OIAQzo2d}.

\bibitem[Valenti et al. (2003)]{valenti-et-al-2003}

Salvatore Valenti, Francesca Neri, and Alessandro Cucchiarelli. \emph{An
Overview of Current Research on Automated Essay Grading}. January 2003. Journal
of Information Technology Education, Vol. 2, No. 1, pp. 319--330.

\bibitem[Ala-Mutka (2005)]{ala-mutka-2005}

Kirsti M. Ala-Mutka. \emph{A Survey of Automated Assessment Approaches for
Programming Assignments}. June 2005. Computer Science Education, Vol. 15, No.
2, pp. 83--102.

\bibitem[Bull \& McKenna (2004)]{bull-mckenna-2004}

Joanna Bull and Colleen McKenna. \emph{Blueprint for Computer-Assisted
Assessment}. 2004. Taylor \& Francis e-Library. Master e-book ISBN:
0-203-46468-0.

\bibitem[Topping (1998)]{topping-1998}

Keith Topping. \emph{Peer Assessment between Students in Colleges and
Universities}. Autumn 1998. Review of Educational Research, Vol. 68, No. 3, pp.
249--276.

\bibitem[Carter et al. (2003)]{carter-et-al-2003}

Janet Carter, John English, Kirsti Ala-Mutka, Martin Dick, William Fone, Ursula
Fuller, Judy Sheard. \emph{How Shall We Assess This?} December 2003. Working
group reports from ITiCSE on Innovation and technology in computer science
education (ITiCSE-WGR '03), David Finkel (Ed.), pp. 107--123.
DOI: 10.1145/960492.960539.

\bibitem[CS Curricula 2013]{cs-curricula-2013}

The Joint Task Force on Computing Curricula. Association for Computing
Machinery (ACM). IEEE Computer Society. \emph{Computer Science Curricula 2013:
Curriculum Guidelines for Undergraduate Degree Programs in Computer Science}.
December 20, 2013. Retrieved from
\url{http://www.acm.org/education/CS2013-final-report.pdf} on March 29, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6ORGeUYy5}.

\bibitem[Skinner (1965)]{skinner-1965}

Burrhus Frederic Skinner. Harvard University. \emph{Reflections on a Decade of
Teaching Machines}. 1965. In Teaching Machines and Programmed Learning, Vol. 2,
Robert Glaser (Ed.), pp. 5--20. National Education Association of the United
States. LCCN: 60-15721.

\bibitem[Kember (1997)]{kember-1997}

David Kember. Hong Kong Polytechnic University. \emph{A Reconceptualisation of
the Research into University Academics' Conceptions of Teaching}. 1997.
Learning and Instruction, Vol. 7, No. 3, pp. 225--275.

\bibitem[Sclater \& Howie (2003)]{sclater-howie-2003}

Niall Sclater and Karen Howie. Center for Educational Systems, University of
Strathclyde, Scotland, UK. \emph{User requirements of the ``ultimate'' online
assessment engine}. April 2003. Computers \& Education, Vol. 40, No. 3, pp.
285--306. DOI: 10.1016/S0360-1315(02)00132-X.

\bibitem[Ohloh (2014)]{ohloh-2014}

Ohloh. Black Duck Software, Inc. Tools. Compare Repositories. Retreived from
\url{http://www.ohloh.net/repositories/compare} on April 12, 2014.

\bibitem[Git (2014)]{git-2014}

Git. \emph{Git and Software Freedom Conservancy.} Retrieved from
\url{http://git-scm.com/sfc} on April 12. 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OmayfnSi}.

\bibitem[GitProjects (2014)]{gitprojects-2014}

GitProjects. \emph{Projects that use Git for their source code management}. Git
Wiki. Last updated on April 5, 2014. Retrieved from
\url{https://git.wiki.kernel.org/index.php/Main_Page} on April 12, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OmbdAIQF}.

\bibitem[gitolite.com (2014a)]{gitolite-com-2014a}

\emph{Hosting git repositories}. Retrieved from
\url{http://gitolite.com/gitolite/index.html} on Arpil 13, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OnsR9f7R}.

\bibitem[gitolite.com (2014b)]{gitolite-com-2014b}

\emph{authentication and authorization in gitolite}. Retrieved from
\url{http://gitolite.com/gitolite/how.html} on Arpil 13, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OoAvdLeK}.

\bibitem[gitolite.com (2014c)]{gitolite-com-2014c}

\emph{who uses gitolite}. Retrieved from
\url{http://gitolite.com/gitolite/who.html} on Arpil 13, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OoB1QVpA}.

\bibitem[gitolite.com (2014d)]{gitolite-com-2014d}

\emph{adding and removing users}. Retrieved from
\url{http://gitolite.com/gitolite/users.html} on Arpil 18, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OvHM2Z2h}.

\bibitem[gitolite.com (2014e)]{gitolite-com-2014e}

\emph{different types of write operations}. Retrieved from
\url{http://gitolite.com/gitolite/write-types.html} on Arpil 18, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OvIKAXXm}.

\bibitem[kernel.org (2014)]{kernel-org-2014}

\emph{How does kernel.org provide its users access to the git trees?}
Frequently asked questions. The Linux Kernel Archives. Retrieved from
\url{https://www.kernel.org/faq.html#whygitolite} on April 13, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OoBgEPwG}.

\bibitem[gitolite Google Group (2011)]{gitolite-google-group-2011}

Dan Carpenter and Sitaram Chamarty. \emph{security audit of Gitolite}.
Discussion on the gitolite Google Group.  First post made on September 30,
2011. Last post made on October 2, 2011. Retrieved from
\url{https://groups.google.com/d/topic/gitolite/jcUkIFKxbQ8/discussion} on
April 13, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OoCHMGop}.

\bibitem[openssh.com (2014)]{openssh-com-2014}

OpenBSD. OpenSSH. Retrieved from \url{http://www.openssh.com/} on April 16,
2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OsQXs51M}.

\bibitem[openssl.org (2014)]{openssl-org-2014}

OpenSSL. Cryptography and SSL/TLS Toolkit. Retrieved from
\url{https://www.openssl.org/} on April 20, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OyQjYQnz}.


\bibitem[ssh(1)]{man-1-ssh}

BSD. \emph{SSH(1)}. ssh — OpenSSH SSH client (remote login program). BSD
General Commands Manual. Published April 6, 2014.  Retrieved from
\url{http://man7.org/linux/man-pages/man1/ssh.1.html} on April 16, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OsTPwEgi}.

\bibitem[sshd(8)]{man-8-sshd}

BSD. \emph{SSHD(8)}. sshd --- OpenSSH SSH daemon. BSD System Manager's Manual.
Published on April 6, 2014. Retrieved from
\url{http://man7.org/linux/man-pages/man8/sshd.8.html} on April 16, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OsTLo4Ce}.

\bibitem[git-shell(1)]{man-1-git-shell}

Git 1.9.rc1. \emph{GIT-SHELL(1)}. git-shell - Restricted login shell for
Git-only SSH access. Git Manual. Published January 30, 2014. Retrieved from
\url{http://man7.org/linux/man-pages/man1/git-shell.1.html} on Arpil 16, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OsZP6SgC}.

\bibitem[git-push(1)]{man-1-git-push}

Git 1.9.rc1. \emph{GIT-PUSH(1)}. git-push - Update remote refs along with
associated objects. Git Manual. Published January 30, 2014. Retrieved from
\url{http://man7.org/linux/man-pages/man1/git-push.1.html} on Arpil 16, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6Ot2V2qp1}.

\bibitem[git-revert(1)]{man-1-git-revert}

Git 1.9.rc1. \emph{GIT-REVERT(1). git-revert - Revert some existing commits.}
Git Manual. Published January 30, 2014. Retrieved from
\url{http://man7.org/linux/man-pages/man1/git-revert.1.html} on Arpil 17, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6Ot6LflKS}.

\bibitem[git-hooks(5)]{man-5-githooks}

Git 1.9.rc1. \emph{GITHOOKS(15). githooks - Hooks used by Git.} Git Manual.
Published January 30, 2014. Retrieved from
\url{http://man7.org/linux/man-pages/man5/githooks.5.html} on Arpil 17, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OtvjunoB}.

\bibitem[clone(2)]{man-2-clone}

Linux. \emph{CLONE(2). \texttt{clone}, \texttt{\_\_clone2} - create a child
process}. Linux Programmer's Manual. Published February 27, 2014. Retrieved
from \url{http://man7.org/linux/man-pages/man2/clone.2.html} on April 21, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6P04xS6aU}.

\bibitem[fork(2)]{man-2-fork}

Linux. \emph{FORK(2). \texttt{fork} - create a child process}. Linux
Programmer's Manual. Published March 12, 2014. Retrieved from
\url{http://man7.org/linux/man-pages/man2/fork.2.html} on April 21, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6P065nmSn}.

\bibitem[proc(5)]{man-5-proc}

Linux. \emph{PROC(2). \texttt{proc} - process information pseudo-filesystem}.
Linux Programmer's Manual. Published April 12, 2014. Retrieved from
\url{http://man7.org/linux/man-pages/man5/proc.5.html} on April 21, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6P0AnUQsS}.

\bibitem[Bird et al. (2009]{bird-et-al-2009}

Christian Bird, Peter C. Rigby, Earl T. Barr, David J. Hamilton, Daniel M.
German, and Prem Devanbu. \emph{The promises and perils of mining git}.
Proceedings of the 2009 6th IEEE International Working Conference on Mining
Software Repositories, pp. 1--10. IEEE Computer Society Washington, DC, USA.
ISBN 978-1-4244-3493-0.

\bibitem[Torvalds (2007)]{torvalds-2007}

Linus Torvalds. \emph{Re: Modify/edit old commit messages}. Retrieved from
\url{http://www.gelato.unsw.edu.au/archives/git/0702/38650.html} on April 17,
2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6Ot2yqQYR}.

\bibitem[Hamano (2009)]{hamano-2009}

Junio C Hamano. In response to ``\emph{How do I push amended commit to the remote
git repo?}'' StackOverflow. Posted on January 11, 2009, under the username
``gitster''. Edited by Gottlieb Notschnabel on September 3, 2013. Retrieved
from \url{http://stackoverflow.com/a/432518/108100} on April 17, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6Ot4dU85N}.

Revision history retrieved from
\url{http://stackoverflow.com/posts/432518/revisions} on April 17, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6Ot4hGKpY}.

\bibitem[Rego (2013)]{rego-2013}

Cauê C. M. Rego. In response to ``\emph{How to properly force a Git Push?}''
StackOverflow. Posted on May 22, 2013, under the username ``Cawas''.  Retrieved
from \url{http://stackoverflow.com/a/16702355/108100} on April 17, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6Ot4qY1Y2}.

\bibitem[cvedetails.com (2014a)]{cvedetails-com-2014a}

CVE Details. The ultimate security vulnerability datasource. \emph{GIT:
Security Vulnerabilities}. Retrieved from
\url{http://www.cvedetails.com/vulnerability-list/vendor_id-4008/GIT.html} on
April 18, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OvKd3HTW}.

\bibitem[cvedetails.com (2014b)]{cvedetails-com-2014b}

CVE Details. The ultimate security vulnerability datasource. \emph{Openssh:
Security Vulnerabilities}. Retrieved from
\url{http://www.cvedetails.com/vulnerability-list/vendor_id-7161/Openssh.html},
on April 18, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OvM6eL7m}.

\bibitem[cvedetails.com (2014c)]{cvedetails-com-2014c}

CVE Details. The ultimate security vulnerability datasource. \emph{Openssl:
Security Vulnerabilities}. Retrieved from
\url{http://www.cvedetails.com/vulnerability-list/vendor_id-217/Openssl.html},
on April 18, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OvMlTlsh}.

\bibitem[cvedetails.com (2014d)]{cvedetails-com-2014d}

CVE Details. The ultimate security vulnerability datasource. \emph{Perl:
Security Vulnerabilities}. Retrieved from
\url{http://www.cvedetails.com/vulnerability-list/vendor_id-1885/Perl.html}, on
April 18, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OvMGTWjE}.

\bibitem[Huang (2013)]{huang-2013}

Jay Huang. \emph{Pushing code to GitHub as Linus Torvalds}. Posted on December
16, 2013. Retrieved from
\url{http://www.jayhuang.org/blog/pushing-code-to-github-as-linus-torvalds/} on
April 18, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OvK7dQBu}.

\bibitem[Gerwitzh (2013)]{gerwitz-2013}

Mike Gerwitz. \emph{A Git Horror Story: Repository Integrity With Signed
Commits}. Last edited on November 10, 2013. Retrieved from
\url{http://mikegerwitz.com/papers/git-horror-story} on April 18, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OvKR8Hzi}.

\bibitem[Homakov (2012)]{homakov-2012}

Egor Homakov. \emph{Hacking rails/rails repo}. Published on March 4, 2012.
Retrieved from \url{http://homakov.blogspot.dk/2012/03/how-to.html} on April
18, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OvLP3zYf}.

\bibitem[Homakov (2014)]{homakov-2014}

Egor Homakov. \emph{How I hacked GitHub again}. Published on February 7, 2014.
Retrieved from
\url{http://homakov.blogspot.dk/2014/02/how-i-hacked-github-again.html} on
April 18, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OvKurm25}.

\bibitem[Hutchings (2011)]{hutchings-2011}

Ben Hutchings. \emph{Accepted linux-2.6 3.0.0\textasciitilde
rc1-1\textasciitilde experimental.1 (source all amd64)}. Email sent to the
Debian Mailing Lists on June 1, 2011.  Retrieved from
\url{http://packages.qa.debian.org/l/linux-2.6/news/20110601T223515Z.html} on
April 25, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6P7kSQe9C}.

\bibitem[Wright et al. (2002)]{wright-et-al-2002}

Chris Wright, Crispin Cowan, Stephen Smalley, James Morris, and Greg
Kroah-Hartman. \emph{Linux Security Modules: General Security Support for the
Linux Kernel}. August 2002. In Proceedings of the 11th USENIX Security
Symposium. USENIX Association. San Francisco, California, United States.
Retrieved from
\url{https://www.usenix.org/legacy/event/sec02/full_papers/wright/wright.pdf}
on April 19, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OxFtc1KV}.

\bibitem[Turner et al. (2010)]{turner-et-al-2010}

Paul Turner, Bharata B Rao, and Nikhil Rao. \emph{CPU bandwidth control for
CFS}. July 2010. In Linux Symposium, Vol 10, pp. 245--254. Ottawa, Ontoria,
Canada. Retrieved from
\url{https://www.kernel.org/doc/ols/2010/ols2010-pages-245-254.pdf} on April
28, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6P9ouxLJJ}.

\bibitem[Linux kernel (v3.14.2)]{linux-kernel-v3.14.2}

The Linux kernel v3.14.2.

Retrieved from
\url{https://www.kernel.org/pub/linux/kernel/v3.x/linux-3.14.2.tar.xz} on April
28, 2014.

Signed by Greg Kroah-Hartman, using the GPG key:

\begin{lstlisting}
pub   4096R/6092693E 2011-09-23
uid     Greg Kroah-Hartman
          (Linux kernel stable release signing key) <greg@kroah.com>
sub   4096R/76D54749 2011-09-23
\end{lstlisting}

Yielding the signature:

\begin{lstlisting}
-----BEGIN PGP SIGNATURE-----
Version: GnuPG v2.0.22 (GNU/Linux)

iQIcBAABAgAGBQJTXE0zAAoJEDjbvchgkmk+0AUQAKrfkqeRXpwePAEHFCBqTqvN
R2fZa6tAY1w5psN8grWh2seu2W1KAtEk53oht/6uZITqs3i2pYmRAJyEzVTBggs9
4BI0rClqebeiO3wkD1biRAIMPQWt6UAB/pvjBeMmMiw4G7FFZHSvBSct91Dsnb87
4A7083ZT/A421C2OtH3vROehyQDyfHp+oL22SKMCoXKCCMCDZp5K07AMVggrzDoZ
KGDEeBpowCSCtoUEEBlrVGz/syyaWZzzcMy+UYeZ12JxpfgnX5oq14w1HIPfAhJn
/P6x7OvmN75oIrxrt4rRs+aUY97iuiEzPpn9F2K4rNruTZUXN7906h/WWCJ/K/b0
D80wC1msaJqMYIEhQICu5kwezVswKVHz3QM9BO1ak3RgObw3j70KKVxJQ95I6jYn
I3uz8RDGXWvp+6aso8vl/HWbQ6dCCA/9plYALJZmRcy2Yg0A0nH3w6+ckC1x/r4l
ZyR6NEcVYg27HQswjmWxbqUhapFMLQGj5oGZ9svbsdwet3ckQTcqAtS5N/YHZZaQ
SnzvY4dZ/MoRwdCGz0hC99RofIgMPgY8ypkc2GGvyGv9uDLsK4koB65ZX1zW/oRw
43eatEoY/Q1QyGWrbwqEWFY91XbZne1KJNwdXYkmTDawMI2F2zApIjsAHpMseJiN
XZPAJqjjAF6nhxRzsrI8
=HZrL
-----END PGP SIGNATURE-----
\end{lstlisting}

\bibitem[resource\_counter.txt]{resource-counter.txt}

Li Zefan, et al.  \emph{The Resource Counter}. Found in
\cite{linux-kernel-v3.14.2}, under \texttt{./Documentation/cgroups/}.

\bibitem[cpuacct.txt]{cpuacct.txt}

Bharata B Rao, et al. \emph{CPU Accounting Controller}.  Found in
\cite{linux-kernel-v3.14.2}, under \texttt{./Documentation/cgroups/}.

\bibitem[memory.txt]{memory.txt}

Li Zefan, et al.  \emph{Memory Resource Controller}. Found in
\cite{linux-kernel-v3.14.2}, under \texttt{./Documentation/cgroups/}.

\bibitem[cgroups.txt]{cgroups.txt}

Paul Menage, Paul Jackson, Chirstoph Lameter, et al. \emph{CGROUPS}.  Found in
\cite{linux-kernel-v3.14.2}, under \texttt{./Documentation/cgroups/}.

\bibitem[sched-design-CFS.txt]{sched-design-cfs.txt}

J. Bruce Fields, et al. \emph{CFS Scheduler}.  Found in
\cite{linux-kernel-v3.14.2}, under \texttt{./Documentation/scheduler/}.

\bibitem[sched-bwc.txt]{sched-bwc.txt}

Bharata B Rao. \emph{CFS Bandwidth Control}.  Found in
\cite{linux-kernel-v3.14.2}, under \texttt{./Documentation/scheduler/}.

\bibitem[sched-rt-group.txt]{sched-rt-group.txt}

J. Bruce Fields. \emph{Real-Time group scheduling}.  Found in
\cite{linux-kernel-v3.14.2}, under \texttt{./Documentation/scheduler/}.

\bibitem[kernel-parameters.txt]{kernel-parameters.txt}

Linus Torvalds, et al. \emph{Kernel Parameters}. Found in
\cite{linux-kernel-v3.14.2}, under \texttt{./Documentation/}.

\bibitem[LSM.txt]{lsm.txt}

Kees Cook. \emph{Linux Security Module Framework}. Found in
\cite{linux-kernel-v3.14.2}, under \texttt{./Documentation/security/}.

\end{thebibliography}
