% vim: set spell:

\begin{thebibliography}{9} % 9 if < 10 references, 99 if < 100 references, etc.

\bibitem[Wheeler, 2007]{why-oss-fs}

David A. Wheeler. \emph{Why Open Source Software / Free Software (OSS/FS,
FLOSS, or FOSS)? Look at the Numbers!}. Revised as of April 16, 2007. Retrieved
from \url{http://www.dwheeler.com/oss_fs_why.html} on March 7, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6NtSnvALX}.

\bibitem[CS2013]{cs2013}

ACM/IEEE-CS Joint Task Force on Computing Curricula. \emph{Computer Science
Curricula 2013}. December 2013. ACM Press and IEEE Computer Society Press.
Retrieved from
\url{http://ai.stanford.edu/users/sahami/CS2013/final-draft/CS2013-final-report.pdf}
on March 7, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6NtTXPH2s}.

\bibitem[EHEA (1999)]{ehea1999}

Joint declaration of the European Ministers of Education. \emph{The Bologna
Declaration}. June 19, 1999. The European Higher Education Area. Retrieved from
\url{http://www.ehea.info/Uploads/Declarations/BOLOGNA_DECLARATION1.pdf} on
March 9, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6Nwr8h8l7}.

\bibitem[CND (2004)]{cnd2004}

Sebastian Horst and Carl Winsløw. \emph{Undervisning i blokstruktur -
potentialer og risici}. April 1, 2004. DidakTips 5. Center for Natufagenes
Didaktik.  University of Copenhagen. Retrieved from
\url{http://www.ind.ku.dk/publikationer/didaktips/didaktips5/5.undervisningiblokstruktur-potentialerogrisicimedomslag.pdf}
on March 9, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6NwjYWlBi}.

\bibitem[BEK 814]{bek814}

Ministeriet for Forskning, Innovation og Videregående Uddannelser.
\emph{Bekendtgørelse om bachelor- og kandidatuddannelser ved universiteterne
(uddannelsesbekendtgørelsen)}. Ministerial Order no. 814 of December 19,
2013.  Retrieved from
\url{https://www.retsinformation.dk/Forms/R0710.aspx?id=160853} on March 9,
2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6NyGHXc4N}.

\bibitem[BEK 1520]{bek1520}

Ministeriet for Forskning, Innovation og Videregående Uddannelser.
\emph{Bekendtgørelse om bachelor- og kandidatuddannelser ved universiteterne
(uddannelsesbekendtgørelsen)}. Ministerial Order no. 1520 of December 19,
2013.  Retrieved from
\url{https://www.retsinformation.dk/Forms/R0710.aspx?id=160853} on March 9,
2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6Nx4DxLGL}.

\bibitem[BEK 666]{bek666}

Ministeriet for Forskning, Innovation og Videregående Uddannelser.
\emph{Bekendtgørelse om eksamen og censur ved universitetsuddannelser
(eksamensbekendtgørelsen)}. Ministerial Order no. 666 of June 24, 2012.
Retrieved from \url{https://www.retsinformation.dk/Forms/R0710.aspx?id=142560}
on March 10, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6NyI0DlqJ}.

\bibitem[BEK 250]{bek250}

Ministeriet for Forskning, Innovation og Videregående Uddannelser.
\emph{Bekendtgørelse om karakterskala og anden bedømmelse ved
universitetsuddannelser (karakterbekendtgørelsen)}. Ministerial Order no. 250
of March 15, 2007.  Retrieved from
\url{https://www.retsinformation.dk/Forms/R0710.aspx?id=29307} on March 11,
2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6NzVOdWtv}.

\bibitem[Curricula (2013)]{faelles-del-ENG}

\emph{The shared section of the BSc and MSc curricula for study programmes at
the Faculty of Science, University of Copenhagen}. September 2013. Retrieved
from
\url{http://www.science.ku.dk/studerende/studieordninger/faelles_sto/Faelles-del-ENG-2013-web.pdf/}
on March 10, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6NyEpPK67}.

\bibitem[Bradfoot \& Black (2004)]{first-ten-years}

Patricia Broadfoot and Paul Black. \emph{Redefining assessment? The first ten
years of assessment in education}. 2004. Assessment in Education: Principles,
Policy \& Practice, Vol. 11, No. 1, pp. 7--26. DOI:
10.1080/0969594042000208976. Retrieved from
\url{https://cmap.helsinki.fi/rid=1G5ND18R4-1QLJN7R-1SB} on March 16, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6O7OhF8LW}.

\bibitem[Pishghadam et al. (2014)]{assessment-and-burnout}

Reza Pishghadam, Bob Adamson, Shaghayegh Shayesteh Sadafian, and Flora L. F.
Kan. \emph{Conceptions of assessment and teacher burnout}. 2014. Assessment in
Education: Principles, Policy \& Practice, Vol. 21, No. 1, pp. 34--51. DOI:
10.1080/0969594X.2013.817382.

\bibitem[Harlen \& James (1997)]{formative-vs-summative}

Wynne Harlen and Mary James. \emph{Assessment and Learning: differences and
relationships between formative and summative assessment}. 1997. Assessment in
Education: Principles, Policy \& Practice, Vol. 4, No. 3, pp. 365--379. DOI:
10.1080/0969594970040304.

\bibitem[Butler (1988)]{butler1988}

Ruth Butler. \emph{Enhancing and understanding intrinsic motivation: the
effects of of task-involving and ego-involving evaluation on interest and
performance}. February 1988. British Journal of Educational Psychology, Vol.
58, No. 1, pp. 1--14.

\bibitem[Sadler (1989)]{sadler1989}

D.Royce Sadler. \emph{Formative assessment and the design of instructional
systems}. June 1989. Instructional Science, Vol. 18, No. 2, pp. 119--144.
Kluwer Academic Publishers. DOI: 10.1007/BF00117714

\bibitem[Bloom et al. (1971)]{bloom1971}

Benjamin S. Bloom, J. Thomas Hastings, and George F. Madaus. \emph{Handbook on
Formative and Summative Evaluation of Student Learning.} 1971. McGraw-Hili,
Inc. United States. Library of Congress Catalog Card Number 75129488. ISBN
0070061149.

\bibitem[Ramaprasad (1989)]{ramaprasad1989}

Arkalgud Rapaprasad. \emph{On the definition of feedback}. January 1989.
Behavioural Science, Vol. 28, No. 1, pp. 8--13.

\bibitem[Black \& William (1998)]{black-william-1998}

Paul Black and Dylan William. \emph{Assessment and Classroom Learning}. 1998.
Assessment in Education: Principles, Policy \& Practice, Vol. 5, No. 1, pp.
7--74. DOI: 10.1080/0969595980050102.

\bibitem[Gibbs \& Simpson (2004)]{gibbs-simpson-2004}

Graham Gibbs and Claire Simpson. \emph{Conditions Under Which Assessment
Supports Students' Learning}. May 2004. Learning and Teaching in Higher
Education, Issue 1. Retrieved from
\url{http://www2.glos.ac.uk/offload/tli/lets/lathe/issue1/issue1.pdf} on March
22, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OGkhvGyE}.

\bibitem[Ramsden (1992)]{ramsden-1992}

Paul Ramsden. \emph{Learning to Teach in Higher Education}. 1992. Routledge.
ISBN 0-415-06415-5.

\bibitem[Conole \& Warburton (2005)]{conole-warburton-2005}

Gr\'ainne Conole and Bill Warburton. \emph{A review of computer-assisted
assessment}. March 2005. The Journal of the Association for Learning Technology
(ALT-J), Research in Learning Technology, Vol. 14, No. 1, pp. 17--31. Retrieved
from
\url{http://www.researchinlearningtechnology.net/index.php/rlt/article/download/10970/12674}
on March 23, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OIAQzo2d}.

\bibitem[Valenti et al. (2003)]{valenti-et-al-2003}

Salvatore Valenti, Francesca Neri, and Alessandro Cucchiarelli. \emph{An
Overview of Current Research on Automated Essay Grading}. January 2003. Journal
of Information Technology Education, Vol. 2, No. 1, pp. 319--330.

\bibitem[Ala-Mutka (2005)]{ala-mutka-2005}

Kirsti M. Ala-Mutka. \emph{A Survey of Automated Assessment Approaches for
Programming Assignments}. June 2005. Computer Science Education, Vol. 15, No.
2, pp. 83--102.

\bibitem[Bull \& McKenna (2004)]{bull-mckenna-2004}

Joanna Bull and Colleen McKenna. \emph{Blueprint for Computer-Assisted
Assessment}. 2004. Taylor \& Francis e-Library. Master e-book ISBN:
0-203-46468-0.

\bibitem[Topping (1998)]{topping-1998}

Keith Topping. \emph{Peer Assessment between Students in Colleges and
Universities}. Autumn 1998. Review of Educational Research, Vol. 68, No. 3, pp.
249--276.

\bibitem[Carter et al. (2003)]{carter-et-al-2003}

Janet Carter, John English, Kirsti Ala-Mutka, Martin Dick, William Fone, Ursula
Fuller, Judy Sheard. \emph{How Shall We Assess This?} December 2003. Working
group reports from ITiCSE on Innovation and technology in computer science
education (ITiCSE-WGR '03), David Finkel (Ed.), pp. 107--123.
DOI: 10.1145/960492.960539.

\bibitem[CS Curricula 2013]{cs-curricula-2013}

The Joint Task Force on Computing Curricula. Association for Computing
Machinery (ACM). IEEE Computer Society. \emph{Computer Science Curricula 2013:
Curriculum Guidelines for Undergraduate Degree Programs in Computer Science}.
December 20, 2013. Retrieved from
\url{http://www.acm.org/education/CS2013-final-report.pdf} on March 29, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6ORGeUYy5}.

\bibitem[Skinner (1965)]{skinner-1965}

Burrhus Frederic Skinner. Harvard University. \emph{Reflections on a Decade of
Teaching Machines}. 1965. In Teaching Machines and Programmed Learning, Vol. 2,
Robert Glaser (Ed.), pp. 5--20. National Education Association of the United
States. LCCN: 60-15721.

\bibitem[Kember (1997)]{kember-1997}

David Kember. Hong Kong Polytechnic University. \emph{A Reconceptualisation of
the Research into University Academics' Conceptions of Teaching}. 1997.
Learning and Instruction, Vol. 7, No. 3, pp. 225--275.

\bibitem[Sclater \& Howie (2003)]{sclater-howie-2003}

Niall Sclater and Karen Howie. Center for Educational Systems, University of
Strathclyde, Scotland, UK. \emph{User requirements of the ``ultimate'' online
assessment engine}. April 2003. Computers \& Education, Vol. 40, No. 3, pp.
285--306. DOI: 10.1016/S0360-1315(02)00132-X.

\bibitem[Ohloh (2014)]{ohloh-2014}

Ohloh. Black Duck Software, Inc. Tools. Compare Repositories. Retreived from
\url{http://www.ohloh.net/repositories/compare} on April 12, 2014.

\bibitem[Git (2014)]{git-2014}

Git. \emph{Git and Software Freedom Conservancy.} Retrieved from
\url{http://git-scm.com/sfc} on April 12. 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OmayfnSi}.

\bibitem[GitProjects (2014)]{gitprojects-2014}

GitProjects. \emph{Projects that use Git for their source code management}. Git
Wiki. Last updated on April 5, 2014. Retrieved from
\url{https://git.wiki.kernel.org/index.php/Main_Page} on April 12, 2014.

Archived by WebCite\textsuperscript{\textregistered}\ at
\url{http://www.webcitation.org/6OmbdAIQF}.

% \bibitem[Cambridge (1997)]{cambridge-1997}

% Rober Audi (general editor). \emph{The Cambridge Dictionary of Philosophy}.
% 1997. Cambridge University Press. Printed in the United States of America.
% ISBN 0-521-40224-7.

\end{thebibliography}
