% vim: set spell:

\chapter{Sandboxing untrusted code}

\begin{quotation}

\footnotesize\sffamily\itshape

\begin{flushright}

Going all the way back to early time-sharing systems, we systems people
regarded the users, and any code they wrote, as the mortal enemies of us and
each other. We were like the police force in a violent slum.

\smallbreak

\upshape

--- ROGER NEEDHAM, IEEE Symposium on Security and Privacy (1999)

\end{flushright}

\end{quotation}

Students submit digital files in response to assignments. Some of these files
may specify executable computer programs. The automatic evaluation of student
submissions constitutes the static and dynamic evaluation of such files. Static
evaluation constitutes executing computer programs specified by the teaching
staff, which read and analyze student files. In addition, dynamic evaluation
includes executing the programs submitted by students.

The student programs may misbehave in a myriad of different ways. The programs
of the teaching staff, although more trustworthy, may also misbehave. If
nothing else, they may undermine the misbehaviour of students. The intent of
this chapter is to discuss the means in which we can mitigate for such
misbehaviour for all parties, and ensure fair service.

In the first section we provide a high-level overview of the technologies that
can be used sandboxing. Here we come to the conclusion that operating-system
level virtualization is a best candidate option. The remainder of the chapter
deals with basic principles in the Linux kernel (version 3.14) that provide
various means of virtualizing and limiting system resources.

\input{sandboxing-untrusted-code/technology-overview}

\input{sandboxing-untrusted-code/control-groups}

\input{sandboxing-untrusted-code/namespaces}

\input{sandboxing-untrusted-code/resource-limits}

\input{sandboxing-untrusted-code/linux-security-modules}

\input{sandboxing-untrusted-code/seccomp}

