% vim: set spell:

\section{Assessment in Education}

\label{section:assessment-in-education}

% Let us assume that a principal goal of education is to bring about learning
% with understanding\cite{formative-vs-summative}.

Assessment, or evaluation, of people is concerned with obtaining information
about their knowledge, attitudes, or skills. Assessment in education is usually
concerned with obtaining information about students and their
learning\footnote{Sometimes, assessment in education is concerned with
evaluating teachers and their teaching --- we will not be concerned with this
form of assessment here.}\cite{ramsden-1992,assessment-and-burnout}. This is
done with the intent of providing feedback or certification, performing
selection or comparison, improving learning processes,
etc.\cite{first-ten-years}.

\subsection{Categorising Assessment}

There are two principal categories of assessment: formative and summative.  The
definition of each category varies somewhat in educational
research\cite{bloom1971, sadler1989, formative-vs-summative}, and their mutual
compatibility is questionable\cite{butler1988}. Our intent is not to advise on
the matter, but to aid in performing an assessment, regardless of the flavour.

Let us adopt a primitive distinction, which still supports the purposes of our
further analysis:

\begin{description}

\item[Formative] \ \\ A student's strengths and weaknesses are documented in
free form. Formative assessments are qualitative and non-standard\-ised: they
are aimed at measuring the quality of a student's learning, rather than whether
they live up to particular criteria. 

\item[Summative] \ \\ A student is ranked on some well-defined scale, at some
well-defined intervals, based on some well-defined criteria. Summative
assessments are often compoundable and comparable. They may allow to deduce
holistic summative assessments of students or groups, quantitatively measure
student progress, etc.

\end{description}

Formative assessment necessitates the ability to perform personalised
assessments, whereas summative assessment demands the ability to specify
standards and perform standardised assessments.

There are other forms of assessment: diagnostic assessment, self-assessment,
peer-assessment, etc. \cite{bull-mckenna-2004,topping-1998}.  These forms of
assessment vary along formative/summative dimensions, but primarily differ in
terms of when, by whom, and of whom the assessment is made.

\subsection{Feedback}

\label{section:assessment-in-computer-science:feedback}

Feedback is information about the difference between the reference level and
the actual level of some parameter which is used to remedy the difference in
some way\cite{ramaprasad1989}.

Feedback is an important bi-product of assessment in
education\cite{black-william-1998}. Ideally, feedback informs the student of
the quality of their work, outlines key errors, provides corrective guidance,
and encourages further student learning. To be so, it is important that
feedback is understandable, timely, and acted upon by
students\cite{gibbs-simpson-2004}.

These requirements are an active area of research in education. One aiding
approach is to use computer-assisted assessment.

\subsection{Computer-Assisted Assessment}

Computer-assisted assessment is the form of assessment performed with the
assistance of computers\cite{conole-warburton-2005}. The benefit of using
computers is ideally, fast, interactive, consistent, and unbiased
assessment\cite{ala-mutka-2005}. The requirement is that the perceived student
performance can be encoded in some useful digital format.

This requirement however, has proven elusive. Free form performances, such as
essays or oral presentations, are still hard to assess
automatically\cite{valenti-et-al-2003}.  On the other hand, it is questionable
in how far easily assessable performances, such as, multiple-choice
questionnaires, are appropriate for assessment in higher
education\cite{conole-warburton-2005}.

We conjecture, that in how far computers can assist in assessment, depends on
how ``rigorous'' the student performance can be expected to be.  We formalise
this notion below.

\subsection{Assignment}

An assignment is a request for someone to perform a particular job.  An
assignment in education is a request for a student to make a performance, and
often, to provide a record thereof. One purpose of an assignment is to provide
a basis for an assessment. The request therefore, often includes a
specification of what the assessment will be based on, and in what time frame
the assignment should be completed in order to be assessed.

\subsection{Submission}

A submission is a record of student performance, submitted for the purposes of
assessment. A digital submission is a digital encoding of such a record.
Digital submissions are amenable to assessment with the assistance of
computers.

\subsection{Rigor}

We say that the more features of interest can be extrapolated from a data
structure using efficient algorithms, the more ``rigorous'' the data structure.
Rigorousness therefore, depends on the features that we are interested in.

A data source is rigorous if the data it delivers is rigorously structured, and
the same suite of algorithms can be used for all the data it delivers. We
conjecture that in how far computers can assist in assessment depends on how
rigorous students, the source of submissions, can be expected to be.

The use of computers for structuring submissions can sometimes provide for high
rigor. For instance, in a multiple-choice test, a computer may present the
student with the questions and options. The student may then respond to the
computer using toggles, and have the computer encode the choices in a tableau.
An assessment then constitutes merely comparing against a reference tableau ---
something computers are notoriously good at.

If instead, the student is asked to write an essay in a natural language,
today's computers can assist with little more than dictionaries, thesauri,
grammar, and mark up. Although this provides for some rigor, natural languages
are at best, somewhat rigorous.  The extent of this ``somewhat'' is the subject
matter of research in natural language processing and automated essay
assessment\cite{valenti-et-al-2003}. Natural languages however, are much more
expressive, allowing for much richer assessment\cite{conole-warburton-2005}.

Beyond where computers can help, it is indeed the question of how rigorous one
can expect the students to be. In some disciplines, such as computer
programming, high rigor can often be expected in submissions. We explore this
notion in the following sections.

% the goal of higher education?

% validity vs. reliability.

% force students to see all feedback?

% Computer-aided assessment


% https://en.wikipedia.org/wiki/Educational_assessment
% https://en.wikipedia.org/wiki/Educational_technology
% https://en.wikipedia.org/wiki/Philosophy_of_education
% https://en.wikipedia.org/wiki/Instructional_theory
% https://en.wikipedia.org/wiki/Educational_theory

% https://en.wikipedia.org/wiki/Computer_aided_assessment
% https://en.wikipedia.org/wiki/E-assessment
% https://en.wikipedia.org/wiki/QTI

% http://www.imsglobal.org/question/index.html

% https://www.brookes.ac.uk/services/ocsld/resources/briefing_papers/p_p_assessment.pdf

% http://www.maasfep.org/spring13/Assessment%26ClassroomLearning_Black%26William.pdf

% http://files.eric.ed.gov/fulltext/ED214952.pdf

%http://www.google.dk/books?hl=en&lr=&id=ZQpUAQAAQBAJ&oi=fnd&pg=PP1&dq=Assessing+student+learning+in+higher+education&ots=iyEc1Evj2D&sig=ZlsuHVag2xcoTDJ2infrzGBbZoE&redir_esc=y#v=onepage&q=Assessing%20student%20learning%20in%20higher%20education&f=false

% https://en.wikipedia.org/wiki/Standards_for_Educational_and_Psychological_Testing

% http://www.ed.ac.uk/schools-departments/institute-academic-development/learning-teaching/staff/advice/researching/publications/experience-of-learning

% assignment text
% tool for testing a submission, providing some automated feedback
% tool for transforming the automated feedback to formal summative and formative feedback.
% summative comments are compoundable.

% per student attempt per exercise we save, their submission, and our summative
% and formative feedback for it.

% the summative feedback, if any, per assignment is defined when the assignment
% is defined, also a flag is given whether the summative feedback should be
% visible to the student or not.

% The feedback kinds is typically something like a scale, or multiple scales.

% ## To define an assignment:
% 1. Provide an assignment text.
% 2. Specify who may submit the assignment -- see group of assignments.
% 3. Specify the sequence of summative feedback kinds to be yielded for every
%    attempt to solve the assignment.
% 4. Specify a means of compounding the summative feedback of all attempts into
%    one holistic summative feedback on an assignment for a submitter.
% 5. Specify which of the summative feedbacks should be visible to the submitter.
% 6. Specify a test tool, providing some raw feedback for an attempt.
% 7. Specify a feedback transformation tool, yielding the said summative
%    and formative feedbacks.
% 8. Specify whether groups are supported.

% The summative feedback is compoundable. The formative feedback is not.

% The summative feedback may be compounded into a progress report - the
% progress report may or may not be made visible to the submitters.

% In all assignments, for all submitters, one type of summative feedback is
% visible to all submitters -- whether or not they have submitted.

% ## A group of assignments is:
% 1. A sequence of assignments.
% 2. A specification of the group of people that may submit the attempts to
%    solve the assignment.

% ## A progress report may be generated for a group of assignments.
% 1. A progress report is individual per pupil. (how about groups?)
% 2. Compound all the holistic summative feedbacks for all assignments into one
%    holistic summative feedback for the group of assignments for the pupil.

% http://psycnet.apa.org/psycinfo/1963-07136-000

% http://www.youtube.com/watch?v=jTH3ob1IRFo

% There is a range of summative data ready for collection when using
% computer-aided assessment. This may be useful in assessment in general.

% Use of computers blurs the definitions of summative and formative feedback
% further. \cite[262--265]{bloom1971}.
