% vim: set spell:

\section{Courses}

A course is a unit of education imparted in a series of learning activities. A
student is someone who is enrolled for a course for the purposes of learning.
A teacher is someone who is enrolled for a course for the purposes of teaching.
Other roles are discussed in a subsequent section.

A course has some predefined knowledge or skills that the students are expected
to acquire by the end of the course. It is the teachers that impart this
knowledge or skills onto the students, in hope that they retain it.

The student performance is typically summatively assessed at the end of a
course --- at least, on a pass/fail/neither basis. A student passes a course,
if the student has shown to have acquired the said knowledge or skills, and
fails otherwise.  A student may neither pass nor fail in various extraordinary
cases, such as the student dropping out of a course before a final assessment.

This superimposes that submissions to particular assignments must be
summatively assessed --- at least, on a pass/fail/neither basis. We say that a
student ``passes'' an assignment, if some submission is assessed as ``passed''.

Formative assessments of submissions are typically conducted throughout the
course to facilitate and courage student learning, and sometimes also at the
end, to facilitate and encourage future learning.

In a subsequent course evaluation, students may assess how well the teachers
performed in their teaching. We will not be concerned with this here.
