% vim: set spell:

\chapter{Introduction}

\begin{quotation}

\footnotesize\sffamily\itshape

\begin{flushright}

In any teaching of the application of computers it is essential to have the
students do practical programming problems and to grade their results. Such
grading should consider both the formal correctness and the performance of the
programs and tends to become difficult and time consuming as soon as the
teaching is beyond the most elementary level.  The possibility of using the
computer to help in this task therefore soon suggests itself.

\smallbreak

\upshape

--- PETER NAUR, {\itshape BIT 4} (1964)

\end{flushright}

\end{quotation}

The above quote gives about as concise an introduction to the subject matter as
we can hope to give. In this chapter, we discuss the problem at hand in greater
depth, and make a few grounding definitions. We discuss what programming
education looks like today, and discuss some of the reasons why this problem
remains open.

Being published in 1964, the quote also indicates that we are about to embark
upon a fairly long-standing problem. We do not hope to solve this problem here.
Our goal is to enable future work by providing a basic framework for
computer-assisted assessment of programming assignments.

If you feel confident about the section headings of this chapter, feel free to
skip it, but consider returning to it, if in doubt about the terminology used
in subsequent chapters.

\input{introduction/assessment-in-education}

\input{introduction/assessment-in-computer-science}

\input{introduction/courses}

\input{introduction/roles-in-educational-assessment}
