% vim: set spell:

\documentclass[a4paper]{article}

\usepackage[a4paper]{geometry}

\usepackage[fancy]{template}
\usepackage{survival-pack}

\setup{%
  subject={Master Project},%
  assignment={Project Description: Online TA},%
  date={February 4, 2014.}%
}
\setupLocation[short=DIKU]{Datalogisk institut, Copenhagen University}
\setupAuthor[addendum={\email{oleks@diku.dk}}]{Oleksandr Shturmov}

\begin{document}

\maketitle
\thispagestyle{first} % no fancy header on first page (just a fancy footer).

We would like to specify and implement an online system for automatically
evaluating submissions to assignments. The prime focus is on programming
assignments, the submissions to which tend to lend their way to automated
evaluation.

The system is meant as an aid to the traditional on-site education at the
Department of Computer Science, University of Copenhagen. The intent of the
system is to aid teachers and their assistants in some of the evaluations they
have to make in the course of a programming course. It would be fair to say
that we would like to design and implement an online teacher's assistant, or
online TA.

The fact that the producers and the consumers of the learning content will be
Computer Science teachers and students, allows us to disregard many of the
problems that would otherwise be worth dealing with, e.g.  graphical user
interfaces. In contrast, the evaluation of submissions to programming
assignments opens the system up to challenging problems and threats. The
automatic evaluation of such submissions typically involves running static or
dynamic analyses of arbitrary student programs.

We would like to ensure that all evaluations run in isolated environments, and
all students get a fair share of system resources. Student programs may run for
too long, use too many resources, fail in unpredictable ways, or even
deliberately attempt to compromise the system. The analyses themselves,
specified by the teachers and their assistants, may behave likewise, except the
lack of incentive to deliberately compromise the system.

It is these problems and threats which are the focus of this project. In the
following sections we further specify the scope of the project, and present the
project-specific learning objectives.

\bigbreak

\textbf{Keywords:} online, automatic evaluation, security engineering,
arbitrary program execution, learning management system.

\input{scope}

%\input{an-online-system}

%\input{arbitrary-program-execution}

%\input{a-basic-learning-management-system}

\input{learning-objectives}

\input{references}

\end{document}

