% vim: set spell:

\section{Roles in Educational Assessment}

There are two principal roles in assessment: the assessing and the assessed.
It is the assessing that define the form of assessment and perform the
assessment itself. It is a matter of ethical concern that the assessed are
sufficiently informed of their assessment and concede to it.

In education, the assessing are often also involved in the role of teaching and
the assessed are often also involved in the role of learning. Those involved in
the role of assessing, but not in teaching, are involved in either censure, or
are interested merely in the summative purposes of an assessment. The assessed,
not involved in the role of learning, are of little interest to us.

\subsection{Teaching}

Teaching is the expediting of learning. Students learn on their own, but
teachers facilitate learning\cite{skinner-1965}. The means of facilitation
however, vary greatly throughout the discipline\cite{ramsden-1992,kember-1997}.
Most however, unite the role of teaching with information delivery and
assessment.

A non-empty set of teachers is always held responsible for a course. Their job
is to make sure that some predefined knowledge or skills is transferred to the
student by the end of the course.

In hope of transferring this knowledge or skills to the student, a teacher
devises means of delivering information about this knowledge or skills, and
devises means of assessing in how far a student possesses this knowledge or
skills. Various techniques in both information delivery and assessment are used
to both facilitate and encourage this transfer.

Since teachers facilitate the education of students, including their
assessment, teachers exert great authority over students. Teachers decide
whether a student passes or fails a course, what grade they get, and how hard
it is for them to get it.

\subsubsection{Teaching assistants}

Teaching assistants assist in teaching responsibilities. They are teaching
subordinates of teachers. They exert some authority over students, but are
often limited in their authority when it comes to important summative
assessments. The result is that teaching assistants perform much of the
formative assessment, and provide guiding remarks either for the purposes of
feedback or to ease important summative assessments for the teachers.

Teaching assistants come about as a scaling mechanism. Once the number of
students enrolled for a course exceeds certain numbers, certain means of
information delivery and assessment are simply infeasible for the teachers
responsible. Instead of hiring more teachers, the strategy is often to rely on
some methods of information delivery and assessment that work in large numbers,
and rely on teaching assistants for the rest. Teaching assistants are therefore
cheaper, less qualified staff that assist in teaching responsibilities.

\subsection{Learning}

Learning is the gaining of knowledge or skills. It is a qualitative change of a
person's view of the world. Individuals engage in learning in hope of being
somehow enlightened or trained for solving particular kinds of problems.

Those engaged in the activity of learning for the purposes of obtaining a
degree are called students.

\subsection{Censure and Summative Assessments}

Censure is a process of quality assurance of assessment. A censor's
participation in an assessment in an assessment varies from mere observation to
avid participation.

\subsection{General Public}

The general public includes those who are ultimately interested in the outcomes
of education and the quality of assessment therein. This includes both
perspective students, future employers, the politically concious, etc.

The general public may be interested in open access to the elements of
education and assessment for the purposes of assessing the quality of
education. The intent may be to see if the education lives up to social
expectations, demands of the labour market, political promises, etc.

Privacy and anonymity is a matter of grave public concern. If open access is
given, it should only identify those who may reasonably be held responsible for
an eventual lack of quality in education. Also, issues of copyright have to be
taken into account.

As the general public would assess education, and not students, students should
not be personally identifiable by the general public. In how far teachers and
teaching assistants may reasonably be held responsible by the general public
for the quality of education may be a matter of university policy (as their
employer). It is important that the assessed are sufficiently informed of their
assessment and have conceded to it.

As students typically own the content they produce, individual student work or
commentary should not be made available to the general public. In how far
teachers and teaching assistants own the content they produce may again be a
matter of university policy (as their employer). It is important that the
owners of content have command over its reproduction.
